\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-10-01 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Modified the bibliography

The inequalities in Eq.\ref{eq:eddingtonFactorBounds} desire more attention than have be given.
They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson [citation], Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2 [citation] may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1 [citation] can be dangerous for both the cases. The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

>>>>

The inequalities in Eq.\ref{eq:eddingtonFactorBounds} desire more attention than have be given.
They have the equal importance as the inequalities in Eq.\ref{eq:MomentsBounds} in preserving the validity of the simulation result.
However, as Fig.~\eqref{fig:EddingtonFactorsWithDifferentClosure} shows, not all the algebraic closures satisfy the Eddington factor bounds Eq.\ref{eq:eddingtonFactorBounds}: Kershaw\cite{kershaw_1976}, Wilson\cite{wilson_1975,leblanc_1970}, Levermore\cite{levermore_1984}, Minerbo \cite{minerbo_1978}, Janka 2\cite{janka_1992} may work fine with neutrino low occupied setting, but not for high occupancy situation; Janka 1\cite{janka_1991} can be dangerous for both the cases. The only algebraic closure that remains in the bounds among those seven plotted closures is Cernohorsky \& Bludman's \cite{cernohorskyBludman_1994}.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_10}
    \includegraphics[width=0.5\textwidth]{figures/Closures0_90}
  \end{tabular}
   \caption{Plot of Eddington factors $\chi$ versus flux factor $h$ for different values of $\cJ$ for various algebraic closures: $\cJ=0.1$ (left panel, low occupied) and $\cJ=0.9$ (right panel, high occupied).  In each panel we plot the Eddington factors of Kershaw (red), Wilson (yellow), Levermore (green), Minerbo (light blue), Cernohorsky \& Bludman (blue) and Janka (purple and pink) closures.  We also plot $\chi_{\mbox{\tiny min}}$ and $\chi_{\mbox{\tiny max}}$ defined in Eq.~\eqref{eq:eddingtonFactorBounds} (lower and upper dash black lines, respectively).}
  \label{fig:EddingtonFactorsWithDifferentClosure}
\end{figure}

### 2018-10-01 Documents/M1/Astronum_2018/sections/intro.tex
Modified the bibliography

\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.}

To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a constraint-preserving diffusion accurate IMEX schemes for ensure a valid result.
Here is the explanation.

@@

Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.

>>>>

\ee{Some background on current ``state-of-the-art'' simulations and the approach they take.} \cite{vartanyan_etal_2018,oConnorCouch_2018,pan_etal_2018,cabezon_etal_2018,glas_etal_2018,just_etal_2018,kuroda_etal_2016}

To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a convex-invariant diffusion accurate IMEX schemes for ensure a valid result.
Here is the explanation.

@@

Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a convex-invariant IMEX.
Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
